tl20-05_berghei_pir_GeneSetEnrichmentQusage

### 2021-10-01 chapter3_results_bergheiPir/Manuscript_berghei_pir_GeneSetEnrichmentQusage.Rmd
Save qusage again

```{r save_xlsx}
to_save <- bind_rows(
  lapply(c(maleGam_v_Asex.Mix.results, 
           maleGam_v_Liv.Meroz.results, 
           Asex.Mix_v_Liv.Meroz.results,
           maleVfemale, 
           post48livvearlyliv, 
           livmero_livpost48.results),
         getElement,
         'qstable')
) %>% 
  select(contrast, everything()) %>% 
  mutate(FDR = p.adjust(p.Value, method = 'fdr')) %>% 
  arrange(contrast, pathway.name)

write_xlsx(to_save,
           path = 'SupplementaryInformation_Stats_Qusage_berghei.xlsx')
write.csv(to_save,
          'SupplementaryInformation_Stats_Qusage_berghei.csv')
```

>>>>

```{r save_xlsx}
write_xlsx(all_stats_df,
           path = 'SupplementaryInformation_Stats_Qusage_berghei.xlsx')
write.csv(all_stats_df,
          'SupplementaryInformation_Stats_Qusage_berghei.csv')
```
